---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/gdorum/relMix/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/gdorum/relMix/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->



# relMix

relMix analyses DNA mixtures involving relatives by computing likelihood ratios that can account for dropout and drop-in, mutations, silent alleles and population substructure. relMix can both be used to make inferences about the relationship between individuals in a DNA mixture such as in non-invasive prenatal paternity testing, and to identify contributors to a mixed DNA stain who may be related. Relationships are represented by pedigrees and can include kinship between more than two individuals. The main function is the graphical user interface ``` relMixGUI```. A tutorial can be found here: https://gdorum.github.io/relMix/articles/relMix.html

## Installation

Install from GitHub as follows:

``` r
 # First install devtools if needed
if(!require(devtools)) install.packages("devtools")
devtools::install_github("gdorum/relMix")
```

To provide pedigree plots, relMix uses the package `tkrplot`. However, this package has some compatibility issues with MacOS and hence is not included as a *hard* dependency. Users who wish to see pedigree plots in the results screen have to install the package `tkrplot` manually with

```{r gh-installation-tkrplot, eval = FALSE}
install.packages("tkrplot")
```

The `tkrplot` package will be loaded by relMix automatially, so users do not need to run `library("tkrplot")` in advance.

